---
graphics: yes
header-includes:
- \usepackage{tabu}
- \usepackage{amssymb, amsmath, amsthm}
- \usepackage{enumerate}
- \renewcommand{\P}{\textrm{P}}
- \newcommand{\R}{\mathbb{R}}
- \newcommand{\E}{\mathbb{E}}
- \newcommand{\var}{{\rm Var}}
- \newcommand{\cov}{{\rm Cov}}
- \newcommand{\iid}{\stackrel{iid}{\sim}}
- \newcommand{\N}{\mathcal{N}}
output: pdf_document
---
\noindent \begin{tabu} to \textwidth {@{}X[4 l] @{}X[r]}
  \textbf{Problem Set 3} 	       & \\ 
  \textbf{Mgmt 237Q: Econometrics} & \\ 
  \textbf{Professor Rossi}		   & 
\end{tabu}
##Garima Agarwal

This problem set is designed to review material on the multiple regression model and time series. Include both your R code and output in your answers.


## Question 1

Rerun the regression of `VWMNFX` on `vwretd`.

a. Compute a 90\% prediction interval using the formulas in the class notes.
b. Check your work in part (a) by computing a 90\% prediction interval using the R `predict` command for `vwretd` = 0.05.
```{r}
library(DataAnalytics)
library(reshape2)
data(Vanguard)
Van=Vanguard[,c(1,2,5)]   # grab relevant cols
V_reshaped=dcast(Van,date~ticker,value.var="mret")

#
# now let's plot mean std deviation.
#
mat=descStat(V_reshaped)
data(marketRf)
Van_mkt=merge(V_reshaped,marketRf,by="date")
with(Van_mkt,
             plot(vwretd,VWNFX,pch=20,col="blue",xlab="vwretd",ylab="VWNFX") 
       )




out=lm(VWNFX~vwretd,data=Van_mkt)
abline(out$coef,col="red",lwd=2)
with(Van_mkt,
     points(mean(vwretd),mean(VWNFX),pch=200,cex=2,col="green") )
summary(out)
lmSumm(out)



```
Using the following formulae
$$1. s_{pred} = s\times\sqrt{\left(1 + \frac{1}{N} + \frac{(X_f - \bar{X})^2}{(N-1)s_x^2}\right)}$$
$$2. y_{upper} = b_0 + b_1X_{f} + t_{N-2,\alpha/2}s_{pred}$$
$$3. y_{lower} = b_0 + b_1X_{f} - t_{N-2,\alpha/2}s_{pred}$$
```{r}
N <- length(Van_mkt$VWNFX[!is.na(Van_mkt$VWNFX)])
see <- sqrt(sum(out$residuals^2)/(N-2))
xf <- 0.05
xbar <- mean(Van_mkt$vwretd,na.rm = "TRUE")
sx <-  sd(Van_mkt$vwretd,na.rm = "TRUE")
spred <-see*sqrt(1 + (1/N) + ((xf-xbar)^2/ ((N-1)*sx^2)) )
tcrit <- qt(0.10/2,N-2)
b0 <- out$coefficients[[1]]
b1 <- out$coefficients[[2]]
y_upper <- b0 + b1*xf + tcrit*spred
y_lower <- b0 + b1*xf - tcrit*spred
cat("The prediction interval for vwretd = 0.05 is",y_upper, "to", y_lower)

p <- predict(out, new = data.frame(vwretd =0.05), int = "prediction", level =0.9)
print(paste0("predicted value using predict is ",p[2]," to ",p[3]," with fitted value as ",p[1]))
```

## Question 2

Using a sequence of simple regressions, show how to obtain the multiple regression coefficient on $P2$ in the multi dataset. 
```{r}
data(multi)
out=lm(p2~p1,data=multi)
e2.1=out$residuals
out2=lm(Sales~e2.1,data=multi)
coef_p2=out2$coefficients[2]
print(paste0("Coefficient of p2 using simple regression is",coef_p2))

# verifying with multiple regression
out3=lm(Sales~p1+p2,data=multi)
print (out3$coefficient[3])
```
as we can see, coefficient from multiple regression is same as the one we obtained using simple regression twice.

## Question 3

This question will ask you to use matrix formulas to compute the variance of a portfolio. Specifically, let:

$$ \mu = \begin{bmatrix} 0.010 \\ 0.015 \\ 0.025 \end{bmatrix} \hspace{1em} \textrm{and} \hspace{1em} \Sigma = \begin{bmatrix} 0.0016 & 0.0010 & 0.0015 \\  & 0.0020 & 0.0019 \\  &  & 0.0042 \end{bmatrix} $$

a. Compute the correlation matrix of these three assets from the variance-covariance matrix $\Sigma$. (Hint: you must divide the $(i,j)$ element of $\Sigma$ by $\sigma_i$ and $\sigma_j$.)
b. Compute the mean and standard deviation of a portfolio made from these assets with weights $(0.3, 0.4, 0.3)$

```{r}
mu=matrix(c(.01,.015,.025),nrow=1)
mu
Covar=matrix(c(.0016,.001,.0015,.001,.002,.0019,.0015,.0019,.0042),nrow=3,ncol=3)
Covar
sigma = matrix(c(1/sqrt(Covar[1,1]),0,0,0,1/sqrt(Covar[2,2]),0,0,0, 1/sqrt(Covar[3,3])),ncol=3)
correl = matrix(rep(NA,9), ncol = 3)
correl = sigma%*%Covar%*%sigma
cat("Correlation Matrix")
correl


wght = matrix(c(0.3, 0.4, 0.3),nrow=1)
wght
#Portfolio mean 
meanport <- wght%*%t(mu)
cat("Mean of portfolio is", meanport)

PortfolioStddev <-sqrt(wght %*% Covar %*% t(wght))
cat("Standard deviation of the portfolio is", PortfolioStddev) 
```
## Question 4

Use matrix formulas to reproduce the least squares coefficients and standard errors shown on slide 17 of Chapter II.
```{r}
data("countryret")

out <- with(countryret, lm(usa~canada+uk+australia+france+germany+japan))
lmSumm(out)
y =countryret$usa
X =cbind(rep(1,length(y)),countryret$canada,countryret$uk,countryret$australia,countryret$france,countryret$germany,countryret$japan)

lm(usa ~ canada+uk+australia+sweden+germany,data=countryret)
#intercept
b =chol2inv(chol(crossprod(X)))%*%crossprod(X,y)
cat("Printing coefficients")
row.names(b)= c("intercept","canada","uk","australia","france","germany","japan")
b
#stderror
e = y- X%*%b
ssq = sum(e*e)/(length(y)- ncol(X))
Var_b = ssq*chol2inv(chol(crossprod(X)))
std_err = sqrt(diag(Var_b))
names(std_err)= c("intercept","canada","uk","australia","france","germany","japan")
cat("Printing the standard error")
std_err
```

## Question 5

Retrieve the Apple stock price series using the `quantmod` package (as done in the notes). Compute the autocorrelation of the difference in log prices.

```{r}
library(quantmod)
getSymbols('AAPL')
y<-AAPL$AAPL.Close
y1<-log(as.vector(y))
y2<-back(y1)
y3<-y1-y2
ds=as.data.frame(c(y1,y2))
lm(y1~y2)
acf(na.omit(y3))[1]
Box.test(y3,type="Ljung",lag=20)
```
