---
title: "Computational_Method_of_Finance_8"
author: "Garima Agarwal"
date: "May 28, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(OptionPricing)
library(plyr)
```

#1
```{r vasicek_functions}
vasicek<-function(r0, sigma, kappa, rbar, T,dt){
  n=T/dt
  npath=500
  r=matrix(data=0,nrow=npath,ncol=(n+1))
  r[,1]=r0
  
  for(i in 2:(n+1)){
    r[,i]=r[,(i-1)] + kappa*(rbar-r[,(i-1)])*dt +sigma*sqrt(dt)*rnorm(npath)
    
  }
  R=dt*rowSums(r)
  r_fin=r[,(n+1)]
  P=mean(exp(-R))
  return(P)
}

vasicek_r<-function(r0, sigma, kappa, rbar, T,dt,npath=500){
  n=T/dt
  
  r=matrix(data=0,nrow=npath,ncol=(n+1))
  r[,1]=r0
  
  for(i in 2:(n+1)){
    r[,i]=r[,(i-1)] + kappa*(rbar-r[,(i-1)])*dt +sigma*sqrt(dt)*rnorm(npath)
    
  }
  R=dt*rowSums(r)
  r_fin=r[,(n+1)]
  P=mean(exp(-R))
  return(cbind(r_fin,R))
}
```

#a

```{r price}
r0 = 0.05
sigma = 0.1
kappa = 0.82
rbar = 0.05
T = 0.5
FV = 1000
dt = 1/360
P=0
price=FV*vasicek(r0, sigma, kappa, rbar, T,dt)
price
```

#b

```{r price_coupon}
time=4
coupon=c(rep(30,7),1030)
T=c(.5,1,1.5,2,2.5,3,3.5,4)
price=vector(length = 8)
for(i in 1:8){
  price[i]=coupon[i]*vasicek(r0, sigma, kappa, rbar, T[i],dt)
}

timeprice=sum(price)
timeprice
```

#c



```{r price_eu}
K=980
t=.25
T=.5
ret=vasicek_r(r0, sigma, kappa, rbar, t,dt)
B=(1-exp(-kappa*(T-t)))/kappa
A=exp((rbar-sigma^2/(2*kappa^2))*(B-(T-t)) - ((sigma^2)*(B^2)/(4*kappa)))
P_t=FV*A*exp(-B*ret[,1])
call=mean(exp(-ret[,2])*pmax((P_t-K),0))
call

```

#d

```{r price_eu_coupon}
r0 = 0.05
sigma = 0.1
kappa = 0.82
rbar = 0.05
K = 980
coupon=c(rep(30,7),1030)
T=c(.5,1,1.5,2,2.5,3,3.5,4)
FV = 1000
dt = 1/360
T= T-0.25
t=0.25
T=as.matrix(T)
set.seed(6)
ret= vasicek_r(r0, sigma, kappa, rbar, t,dt,200)
price=vector(length = length(ret[,1]))
for(i in 1:length(ret[,1])){
  
  #pv=vector(length = 8)
  pv=coupon*apply(T,1,vasicek,r0=ret[i,1],sigma=sigma,kappa=kappa,rbar=rbar,dt=dt)
  # for(j in 1:8){
  #   pv[j]=coupon[j]*vasicek(ret[i,1],sigma,kappa,rbar,T[j],dt)
  # }
  price[i]=sum(pv)
}
call=mean(exp(-ret[,2])*pmax((price-K),0))
call
```

#e

```{r}
T=c(.5,1,1.5,2,2.5,3,3.5,4)


  A<-function(t,T){
    f=exp((rbar-(sigma^2)/(2*kappa^2))*(B(t,T)-(T-t))-((sigma^2)*(B(t,T)^2)/(4*kappa)))
    return (f)
  }
  B<-function(t,T){
    f=(1-exp(-kappa*(T-t)))/kappa
    return (f)
  }
  P<-function(t,T,r){
    p=A(t,T)*exp(-B(t,T)*r)
  }
f<-function(r){
   pr=P(t,T,r)
  sqrt(mean((sum(coupon*P(t,T,r))-K)^2))
}
y=optimize(f,c(0,1))
r=y$minimum
k=P(t,T,r)
ti=T
  
sigmap = (sigma/kappa)*(1-exp(-kappa*(T-t)))*sqrt((1-exp(-2*kappa*t))/(2*kappa))
  
PtTi = P(0,T,r0)
PtT = P(0,t,r0)
  
d1 = 1/sigmap*log(PtTi/(k*PtT))+.5*sigmap
d2 = d1 - sigmap
   # Price of the individual options.
c=sum(coupon*(PtTi*pnorm(d1)-k*PtT*pnorm(d2)))
c
```

Both methods result in very similar values. Monte Carlo takes too much time to run compared to the second technique.

#2

```{r cir_function}
cir<-function(r0, sigma, kappa, rbar, T,dt){
  n=T/dt
  npath=500
  r=matrix(data=0,nrow=npath,ncol=(n+1))
  r[,1]=r0
  
  for(i in 2:(n+1)){
    r[,i]=r[,(i-1)] + kappa*(rbar-r[,(i-1)])*dt +sigma*sqrt(pmax(r[,(i-1)],0))*sqrt(dt)*rnorm(npath)
    
  }
  R=dt*rowSums(r)
  r_fin=r[,(n+1)]
  P=mean(exp(-R))
  return(P)
}

cir_r<-function(r0, sigma, kappa, rbar, T,dt){
  n=T/dt
  npath=500
  r=matrix(data=0,nrow=npath,ncol=(n+1))
  r[,1]=r0
  
  for(i in 2:(n+1)){
    r[,i]=r[,(i-1)] + kappa*(rbar-r[,(i-1)])*dt + sigma*sqrt(pmax(r[,(i-1)],0))*sqrt(dt)*rnorm(npath)
    
  }
  R=dt*rowSums(r)
  r_fin=r[,(n+1)]
  P=mean(exp(-R))
  return(cbind(r_fin,R))
}
AB<-function(T, h1, h2, h3){
    A = (h1*exp(h2*(T))/(h2*(exp(h1*(T))-1)+ h1))^h3
    B = (exp(h1*(T))-1)/(h2*( exp(h1*(T)) - 1 ) + h1)
    return(c(A,B))
}
ifd<-function(r0,sigma,kappa, rbar,T, dr,dt,rmin,rmax, FV, K){
  npath=round(((rmax-rmin)/dr)+1)
  nstep=(T/dt)+1
  
  r=vector(length = npath)
  r[1]=rmax
  for(i in 1:npath){
    r[i]=rmax-(i-1)*dr
  }
  h1=sqrt((kappa^2) + 2*(sigma^2))
  h2=(kappa + h1)/2
  h3=(2*kappa*rbar)/(sigma^2)
  ss=AB(T,h1,h2,h3)
  a1=ss[1]
  b1=ss[2]
  prc_ts=vector(length = npath)
  prc_ts=FV*a1*exp(-b1*(r))
  
  a=matrix(data=0,nrow=npath,ncol=npath)
  a[1,1]=1
  a[1,2]=-1
  a[npath,npath]=-1
  a[npath,(npath-1)]=1
  
  for(i in 2:(npath-1)){
    a[i,(i-1)]=(-dt/(2*dr))*(((sigma^2)*(npath-i+1)) + kappa*(rbar - dr*(npath- i+ 1)))
    a[i,i]=1 + ((dt/dr)*(sigma^2)*(npath-i+1)) + (dr*dt*(npath-i+1))
    a[i,(i+1)]=(-dt/(2*dr))*(((sigma^2)*(npath-i+1))-kappa*(rbar- dr*(npath-i+1)))
  }
  f=matrix(data=0,nrow=npath,ncol=nstep)
  f[,nstep]=pmax((prc_ts-K),0)
  inv_a=solve(a)
  b=vector(length = npath)
  for(j in (nstep-1):1){
    b=f[,(j+1)]
    b[1]=prc_ts[1]-prc_ts[2]
    b[npath]=0
    f[,j]=inv_a%*%b
  }
  call=f[51,1]
  return (call)
}
```

#a
```{r cir_price}
r0 = 0.05
sigma = 0.12
kappa = 0.92
rbar = 0.055
T = 0.5
S = 1
FV = 1000
n= 100
K = 980
timeleft = S-T
dt=T/n
set.seed(0)
ret=cir_r(r0,sigma,kappa,rbar,T,dt)
npath=nrow(ret)
rt=ret[,1]
rt=as.matrix(rt)
#price=vector(length = npath)
price=FV*apply(rt,1,cir,sigma=sigma,kappa=kappa,rbar=rbar,dt=dt,T=timeleft)
call_cir=mean(exp(-ret[,2])*pmax((price-K),0))
call_cir
#price
cir=matrix(nrow=3,ncol=1)
cir[1,1]=call_cir


```

#b

```{r ifd}
r0 = 0.05
sigma = 0.12
kappa = 0.92
rbar = 0.055
T = 0.5
S = 1
FV = 1000
K = 980
rmin = 0
rmax = 0.1
dr = 0.001
dt = 1/360

call_ifd=ifd(r0,sigma,kappa, rbar,T, dr,dt,rmin,rmax, FV, K)
cir[2,1]=call_ifd
call_ifd
```

#c

```{r}
h1 = sqrt((kappa^2) + 2*(sigma^2))
h2 = (kappa + h1)/ 2
h3 = (2*kappa*rbar)/ (sigma^2)
T = 0.5
S = 1
K = 0.98
L = 1000
Strike = 980

ss=AB((S-T),h1,h2,h3)
a=ss[1]
b=ss[2]

r=log(a/K)/b
theta=sqrt((kappa^2) + 2*(sigma^2))
phi=2*theta/((sigma^2)*(exp(theta*T)-1))
zeta=(kappa+theta)/(sigma^2)

ss=AB((S),h1,h2,h3)
a1=ss[1]
b1=ss[2]
p_ts=a1*exp(-b1*r0)

ss=AB((T),h1,h2,h3)
a2=ss[1]
b2=ss[2]
p_tt=a2*exp(-b2*r0)

x1=2*r*(phi+zeta+b)
p1=(4*kappa*rbar/(sigma^2))
q1=(2*(phi^2)*r0*exp(theta*T))/(phi+zeta+b)
chi1=pchisq(x1,p1,q1)

x2=2*r*(phi+zeta)
p2=p1
q2=(2*(phi^2)*r0*exp(theta*T))/(phi+zeta)
chi2=pchisq(x2,p2,q2)

ctTS=L*p_ts*chi1 - (Strike*chi2*p_tt)
cir[3,1]=ctTS
ctTS
rownames(cir)<-c("Monte carlo","IFD","Closed form")
kable(cir)
```

As we can see the values are almost similar thus proving the worth of all the methods. As we can observe, monte carlo takes the longest time and IFD has a higher convergence rate.

#3
```{r g2_function}
generateV<-function(T, a,b, sigma,n,p){
    V1 = ((sigma^2)*(T + (2*exp(-a*T)/a) - (exp(-2*a*T)/(2*a)) - (3/(2*a))))/(a^2)
    V2 = ((n^2)*(T + (2*exp(-b*T)/b) - (exp(-2*b*T)/(2*b)) - (3/(2*b))))/(b^2)
    V3 = (2*p*sigma*n*(T + ((exp(-a*T) - 1)/a) + ((exp(-b*T) - 1)/b) - ((exp(-(a+b)*T) - 1)/(a+b))))/(a*b)
    V = V1 + V2 + V3
    return (V)
}
g2<-function(p,a,b,sigma,x0,y0,n,phi_t,T){
  nstep=180
  dt=T/nstep
  npath=500
  r=matrix(data=0,nrow=npath,ncol=(nstep+1))
  x=matrix(data=0,nrow=npath,ncol=(nstep+1))
  y=matrix(data=0,nrow=npath,ncol=(nstep+1))
  x[,1]=x0
  y[,1]=y0
  r[,1]=.03
  
  for(i in 2:(nstep+1)){
    z1=rnorm(npath)
    z2=rnorm(npath)
    zz2=p*z1 + sqrt(1-(p^2))*z2
    
      x[,i]=x[,(i-1)]-(a*x[,(i-1)]*dt) + (sigma*sqrt(dt)*z1)
      y[,i]=y[,(i-1)] - (b*y[,(i-1)]*dt) + (n*sqrt(dt)*zz2)
      r[,i]=(x[,i]+y[,i] +phi_t)
  }
  R=dt*rowSums(r)
  x_fin=x[,(nstep+1)]
  y_fin=y[,(nstep+1)]
  p=mean(exp(-R))
  return (p)
}

g2_r<-function(p,a,b,sigma,x0,y0,n,phi_t,T){
  nstep=180
  dt=T/nstep
  npath=500
  r=matrix(data=0,nrow=npath,ncol=(nstep+1))
  x=matrix(data=0,nrow=npath,ncol=(nstep+1))
  y=matrix(data=0,nrow=npath,ncol=(nstep+1))
  x[,1]=x0
  y[,1]=y0
  r[,1]=.03
  for(i in 2:(nstep+1)){
    z1=rnorm(npath)
    z2=rnorm(npath)
    zz2=p*z1 + sqrt(1-(p^2))*z2
    
      x[,i]=x[,(i-1)]-(a*x[,(i-1)]*dt) + (sigma*sqrt(dt)*z1)
      y[,i]=y[,(i-1)] - (b*y[,(i-1)]*dt) + (n*sqrt(dt)*zz2)
      r[,i]=(x[,i]+y[,i] + phi_t)
  }
  R=dt*rowSums(r)
  x_fin=x[,(nstep+1)]
  y_fin=y[,(nstep+1)]
  p=mean(exp(-R))
  return (cbind(x_fin,y_fin,R))
}
```

```{r g2_price, eval=TRUE}
x0 = 0
y0 = 0
r0 = 0
phi0 = 0
p = 0.7
a = 0.1
b = 0.3
sigma = 0.03
n = 0.08
phi_t = 0.03
K = 950
K1 = 0.95
T = 0.5
FV = 1000
S = 1
set.seed(2)
ret=g2_r(p,a,b,sigma,x0,y0,n,phi_t,T)
#ret
price=vector(length = nrow(ret))
for(i in 1:nrow(ret)){
  price[i]=FV*g2(p,a,b,sigma,ret[i,1],ret[i,2],n,phi_t,T)
}
#price
eu_put=mean(exp(-ret[,3])*pmax((K-(price)),0))
put=matrix(nrow=2,ncol=1)
put[1,1]=eu_put
eu_put
#plot(ret[,3])
```

```{r}
V_tT = generateV(T, a,b, sigma,n,p)
V_tS = generateV(S, a,b, sigma,n,p)

P_tT = exp((-phi_t*T) - ((1- exp(-a*T))/a)*x0 - ((1- exp(-b*T))/b)*y0 + V_tT/2)
P_tS = exp((-phi_t*S) - ((1- exp(-a*S))/a)*x0 - ((1- exp(-b*S))/b)*y0 + V_tS/2)

SIGMA1 = ((sigma^2)*( (1- exp(-a*(S-T)))^2 )* (1 - exp(-2*a*T)))/(2*(a^3))
SIGMA2 = ((n^2)*( (1- exp(-b*(S-T)))^2 )* (1 - exp(-2*b*T)))/(2*(b^3))
SIGMA3 = (2*p*sigma*n*(1- exp(-a*(S-T)))*(1- exp(-b*(S-T)))*(1- exp(-T*(a+b))))/(a*b*(a+b))
SIGMASQ = SIGMA1 + SIGMA2 + SIGMA3
SIGMA = sqrt(SIGMASQ)

d1 = (log((K1*P_tT)/(P_tS))/SIGMA) - SIGMA/2
d2 = (log((K1*P_tT)/(P_tS))/SIGMA) + SIGMA/2

L = 1000
PtTSK = -L*P_tS*pnorm(d1) + P_tT*K*pnorm(d2)
put[2,1]=PtTSK
PtTSK
kable(put)
```

As we can observe, both values are really close thus proving our Monte-carlo method good.