---
title: "Computational_4"
author: "Garima Agarwal"
date: "May 10, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(OptionPricing)
library(plyr)

lgm<-function(n){
  m = (2^31) - 1
  a = (7^5)
  x=vector(length = (n+1))
  u=vector(length = n)
  x[1]=as.numeric(Sys.time())
  for(i in 2:(n+1))
  {
    x[i] = (a*x[i - 1])%%m
    u[i-1] = (x[i]+0.5)/(m)
  }
  
  return (u)
}
box<-function(u1,u2){
  z1=((-2*log(u1))^(1/2))*cos(2*pi*u2)
  z2=((-2*log(u1))^(1/2))*sin(2*pi*u2)
  return(z1)
}
```


Functions
```{r Function_LSMC}
lsmc<-function(s0,r,n,h,sigma,nstep,t,k,x,method){
  stock=matrix(data=1,nrow=(nstep),ncol=(n+1))
  stock[,1]=s0
  z1=matrix(nrow=(nstep/2),ncol=n)
  for(i in 1:(nstep/2)){
    z1[i,]=box(lgm(n),lgm(n))
    stock[i,2:(n+1)]=exp((r-sigma^2)*h + sigma*sqrt(h)*z1[i,])
    
    stock[i,]=cumprod(stock[i,])
  }
  for(i in ((nstep/2)+1):(nstep)){
    
    stock[i,2:(n+1)]=exp((r-sigma^2)*h + sigma*sqrt(h)*(-z1[(i-(nstep/2)),]))
    stock[i,]=cumprod(stock[i,])
  }
  
  discount=vector(length = n)
  for(i in 1:n){
    discount[i]=exp(-r*(h*i))
  }
  exercise=pmax((x-stock[,2:(n+1)]),0)
  
  option=matrix(data=0,nrow=nstep,ncol=n)
  option[,n]=exercise[,n]
  ind=matrix(data=0,nrow=nstep,ncol=n)
  ind[(exercise[,n]>0),n]=1
  continuation=matrix(data=0,nrow=nstep,ncol=n)
  for(j in n:2){
    y_vector=matrix(data=0,nrow=nstep,ncol=1)
    l_mat=matrix(data=0,nrow=nstep,ncol=k)
    for(i in j:n){
      y_vector=y_vector+ind[,i]*exercise[,i]*exp(-r*h*(j-i))
    }
    #L_mat for Hermite
    if(method==1){
    if(k==2){
      l_mat[,1]=rep(1,times=nstep)
      l_mat[,2]=2*stock[,j]
    }
    if(k==3){
      l_mat[,1]=rep(1,times=nstep)
      l_mat[,2]=2*stock[,j]
      l_mat[,3]=(4*(stock[,j]^2))-2
    }
    if(k==4){
      l_mat[,1]=rep(1,times=nstep)
      l_mat[,2]=2*stock[,j]
      l_mat[,3]=(4*(stock[,j]^2))-2
      l_mat[,4]=(8*(stock[,j]^3))-(12* stock[,j])
    }
    }
    #L_mat for Laguerre
    if(method==2){
    if(k==2){
      l_mat[,1]=(exp(-stock[,(j+1)]/2))
      l_mat[,2]=(exp(-stock[,(j+1)]/2)*(1-stock[,(j+1)]))
    }
    if(k==3){
      l_mat[,1]=(exp(-stock[,(j+1)]/2))
      l_mat[,2]=(exp(-stock[,(j+1)]/2)*(1-stock[,(j+1)]))
      l_mat[,3]=(exp(-stock[,(j+1)]/2)*(1-2*stock[,(j+1)]+((stock[,(j+1)]^2)/2)))
    }
    if(k==4){
      l_mat[,1]=(exp(-stock[,(j+1)]/2))
      l_mat[,2]=(exp(-stock[,(j+1)]/2)*(1-stock[,(j+1)]))
      l_mat[,3]=(exp(-stock[,(j+1)]/2)*(1-2*stock[,(j+1)]+((stock[,(j+1)]^2)/2)))
      l_mat[,4]=(exp(-stock[,(j+1)]/2)*(1-3*stock[,(j+1)]+
                                          (3*(stock[,(j+1)]^2)/2)-((stock[,(j+1)]^3)/6)))
    }      
    }
    #L_mat for Monomial
    if(method==3){
    if(k==2){
      l_mat[,1]=rep(1,times=nstep)
      l_mat[,2]=2*stock[,j]
    }
    if(k==3){
      l_mat[,1]=rep(1,times=nstep)
      l_mat[,2]=stock[,j]
      l_mat[,3]=stock[,j]^2
    }
    if(k==4){
      l_mat[,1]=rep(1,times=nstep)
      l_mat[,2]=2*stock[,j]
      l_mat[,3]=stock[,j]^2
      l_mat[,4]=stock[,j]^3
    }
    }
    A=t(t(l_mat)%*%l_mat)
    b=t(l_mat)%*%y_vector
 #   a=chol2inv(chol(A))%*%(b)
    a=lm(b~A+0)$coef
    a[is.na(a)]<-0
    a=as.matrix(a)
    continuation[,j]=l_mat%*%a
    for(i in 1:nstep){
      if(exercise[i,j]>continuation[i,j]){
        ind[i,j]=1
        if(j<n){
          ind[i,((j+1):n)]=0
        }
      }
    }
  }
  discount_factor=matrix(data=0,nrow=nstep,ncol=n)
  for(i in 1:nstep){
    discount_factor[i,]=discount
  }
  option = (ind*(discount_factor))*(exercise)
  return(sum(option)/nstep)
}
```

#1
#a)
```{r Laguerre}
sigma=.2
r=0.06
s0=40
x=40
n=20
nstep=100000
t=c(.5,1,2)
s0=c(36,40,44)
k=c(2,3,4)
option_36=matrix(data=0,nrow=length(t),ncol=length(k))
option_40=matrix(data=0,nrow=length(t),ncol=length(k))
option_44=matrix(data=0,nrow=length(t),ncol=length(k))
for(j in 1:3){
for(i in 1:3){
  h=t[i]/n
  option_36[i,j]=lsmc(s0[1],r,n,h,sigma,nstep,t[i],k[j],x,2)
}
}
for(j in 1:3){
for(i in 1:3){
  h=t[i]/n
  option_40[i,j]=lsmc(s0[2],r,n,h,sigma,nstep,t[i],k[j],x,2)
}
}
for(j in 1:3){
for(i in 1:3){
  h=t[i]/n
  option_44[i,j]=lsmc(s0[3],r,n,h,sigma,nstep,t[i],k[j],x,2)
}
}
rownames(option_36)<-c("Time=.5","Time=1","Time=2")
rownames(option_40)<-c("Time=.5","Time=1","Time=2")
rownames(option_44)<-c("Time=.5","Time=1","Time=2")
colnames(option_36)<-c("k=2","k=3","k=4")
colnames(option_40)<-c("k=2","k=3","k=4")
colnames(option_44)<-c("k=2","k=3","k=4")
kable(option_36,caption="For stock price 36")
kable(option_40,caption="For stock price 40")
kable(option_44,caption="For stock price 44")

```

#b)

```{r Hermite}
option_36=matrix(data=0,nrow=length(t),ncol=length(k))
option_40=matrix(data=0,nrow=length(t),ncol=length(k))
option_44=matrix(data=0,nrow=length(t),ncol=length(k))
for(j in 1:3){
for(i in 1:3){
  h=t[i]/n
  option_36[i,j]=lsmc(s0[1],r,n,h,sigma,nstep,t[i],k[j],x,1)
}
}
for(j in 1:3){
for(i in 1:3){
  h=t[i]/n
  option_40[i,j]=lsmc(s0[2],r,n,h,sigma,nstep,t[i],k[j],x,1)
}
}
for(j in 1:3){
for(i in 1:3){
  h=t[i]/n
  option_44[i,j]=lsmc(s0[3],r,n,h,sigma,nstep,t[i],k[j],x,1)
}
}
rownames(option_36)<-c("Time=.5","Time=1","Time=2")
rownames(option_40)<-c("Time=.5","Time=1","Time=2")
rownames(option_44)<-c("Time=.5","Time=1","Time=2")
colnames(option_36)<-c("k=2","k=3","k=4")
colnames(option_40)<-c("k=2","k=3","k=4")
colnames(option_44)<-c("k=2","k=3","k=4")
kable(option_36,caption="For stock price 36")
kable(option_40,caption="For stock price 40")
kable(option_44,caption="For stock price 44")
```

#c)

```{r Monomials}
option_36=matrix(data=0,nrow=length(t),ncol=length(k))
option_40=matrix(data=0,nrow=length(t),ncol=length(k))
option_44=matrix(data=0,nrow=length(t),ncol=length(k))
for(j in 1:3){
for(i in 1:3){
  h=t[i]/n
  option_36[i,j]=lsmc(s0[1],r,n,h,sigma,nstep,t[i],k[j],x,3)
}
}
for(j in 1:3){
for(i in 1:3){
  h=t[i]/n
  option_40[i,j]=lsmc(s0[2],r,n,h,sigma,nstep,t[i],k[j],x,3)
}
}
for(j in 1:3){
for(i in 1:3){
  h=t[i]/n
  option_44[i,j]=lsmc(s0[3],r,n,h,sigma,nstep,t[i],k[j],x,3)
}
}
rownames(option_36)<-c("Time=.5","Time=1","Time=2")
rownames(option_40)<-c("Time=.5","Time=1","Time=2")
rownames(option_44)<-c("Time=.5","Time=1","Time=2")
colnames(option_36)<-c("k=2","k=3","k=4")
colnames(option_40)<-c("k=2","k=3","k=4")
colnames(option_44)<-c("k=2","k=3","k=4")
kable(option_36,caption="For stock price 36")
kable(option_40,caption="For stock price 40")
kable(option_44,caption="For stock price 44")
```

#d)

As we can observe, for small values of k, i.e. with less polynomials to predict the values between the 3 methods fluctuate, but as we go closer to using k=4 polynomials the values converge to the the same number pointing it out that using more polynomials lead to better prediction results.

We can clearly see the regular patern of put where the Stock price is In the Money has higher price whereas the stock which is out-of-the-money has lower prices in general.
Also we see that with increase in time, our option prices increasing to accomodate for the chances of a stock getting in the money along the path.


#2

#a)
```{r forwardput}
forwardput<-function(s0,r,n,h,sigma,nstep,t,T){
  t=t*n + 1
  stock=matrix(data=1,nrow=(nstep),ncol=(n+1))
  stock[,1]=s0
  z1=matrix(nrow=(nstep/2),ncol=n)
  for(i in 1:(nstep/2)){
    z1[i,]=box(lgm(n),lgm(n))
    stock[i,2:(n+1)]=exp((r-sigma^2)*h + sigma*sqrt(h)*z1[i,])
    
    stock[i,]=cumprod(stock[i,])
  }
  for(i in ((nstep/2)+1):(nstep)){
    
    stock[i,2:(n+1)]=exp((r-sigma^2)*h + sigma*sqrt(h)*(-z1[(i-(nstep/2)),]))
    stock[i,]=cumprod(stock[i,])
  }
  payoff=pmax((stock[,t]-stock[,(n+1)]),0)
  pay=exp(-r*T)*mean(payoff)
  return(pay)
}
s0=65
x=60
sigma=.2
r=0.06
t1=0.2
T=1
n=100
h=T/n
nstep=500


forward=forwardput(s0,r,n,h,sigma,nstep,t1,T)
forward
```

#b)

```{r}
nstep=100
st=s0*(exp((r-((sigma^2)/2))*t1 + sigma*sqrt(t1)*box(lgm(nstep),lgm(nstep))))
s0_new=mean(st)
t_new=T-t1
price=vector(length = nstep)
h=t_new/n
n_new=20
for(i in 1:nstep){
  price[i]=lsmc(st[i],r,n,h,sigma,n_new,t_new,4,st[i],3)
}
pr=exp(-r*t1)*mean(price)
t<-c(forward,pr)
t=as.matrix(t)
rownames(t)<-c("European Forward Put","American Forward Put")
kable(t)
```