---
title: "Computational_4"
author: "Garima Agarwal"
date: "May 2, 2017"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Function}
binum<-function(S0,X,r,T,sigma,u,d,h,n,p){
  price=vector(length = (n+1))
  option=matrix(nrow = (n+1),ncol=(n+1))
  price[1]=S0
  for(i in 1:length(price)){
    price[i]=S0*(u^(n+1-i))*(d^(i-1))
    option[(n+1),(i)]=max(0,(price[i]-X))
  }
  for(i in 1:n){
    for(j in 1:(n-i+1)){
      option[(n-i+1),j]=exp(-r*h)*(p*option[(n-i+2),j] + (1-p)*option[(n-i+2),(j+1)])
    }
  }
  return (option[1,1])
  
  
}

binum_p_e<-function(S0,X,r,T,sigma,u,d,h,n,p){
  price=vector(length = (n+1))
  option=matrix(nrow = (n+1),ncol=(n+1))
  price[1]=S0
  for(i in 1:length(price)){
    price[i]=S0*(u^(n+1-i))*(d^(i-1))
    option[(n+1),(i)]=max(0,(X-price[i]))
  }
  for(i in 1:n){
    for(j in 1:(n-i+1)){
      
      option[(n-i+1),j]=exp(-r*h)*(p*option[(n-i+2),j] + (1-p)*option[(n-i+2),(j+1)])
    }
  }
  return (option[1,1])
  
  
}
binum_p_a<-function(S0,X,r,T,sigma,u,d,h,n,p){
  price=vector(length = (n+1))
  option=matrix(nrow = (n+1),ncol=(n+1))
  price[1]=S0
  for(i in 1:length(price)){
    price[i]=S0*(u^(n+1-i))*(d^(i-1))
    option[(n+1),(i)]=max(0,(X-price[i]))
  }
  price_l=matrix(nrow = (n+1),ncol=(n+1))

  price_l[1,1]=S0
  for(j in 2:(n+1))
  {
    for(k in 1:j)
    {
    price_l[k,j] <- S0*(u^(j-k))*(d^(k-1))
    }
  }
  price_l=t(price_l)
  optiont=matrix(nrow = (n+1),ncol=(n+1))
  optiont[(n+1),]=option[(n+1),]
  for(i in 1:n){
    for(j in 1:(n-i+1)){
      optiont[(n-i+1),j]=exp(-r*h)*(p*option[(n-i+2),j] + (1-p)*option[(n-i+2),(j+1)])
      option[(n-i+1),j]=max(optiont[(n-i+1),j],(X-price_l[(n-i+1),j]))
    }
  }
  return (option[1,1])
  
  
}

halton<-function(n,m){
  s=vector(length = n)
  num=1+ceiling(log(n)/log(m))
  vet=m^(-(1:num))
  work=vector(length = num)
  for(i in 1:n){
    j=1
    ok=0
    while(ok==0){
      work[j]=work[j]+1
      if(work[j]<m){
        ok=1
      }
      else{
        work[j]=0
        j=j+1
      }
    }
    s[i]=t(vet)%*%(work)
  }
  return(s)
  
}
```

#1
```{r}
S0 = 32
X = 30
r = 0.05
sigma = 0.24
T = 0.5
n=c(10, 20, 40, 80, 100, 200, 500)
price=matrix(nrow = length(n),ncol=4)
#a)
for(i in 1:length(n)){
  h=T/n[i]
  c=0.5*(exp(-r*h)+exp((r+(sigma^2))*h))
  d=c- sqrt((c^2)-1)
  u=1/d
  p=(exp(r*h)-d)/(u-d)
  price[i,1]=binum(S0,X,r,T,sigma,u,d,h,n[i],p)
}
plot(n,price[,1],type="b",col="Red",pch=2,ylim=c(3.7,3.8))
par(new=TRUE)
#b)
for(i in 1:length(n)){
  h=T/n[i]
  u=exp(r*h)*(1+sqrt((exp((sigma^2)*h))-1))
  d=exp(r*h)*(1-sqrt((exp((sigma^2)*h))-1))
  p=0.5
  price[i,2]=binum(S0,X,r,T,sigma,u,d,h,n[i],p)
}
plot(n,price[,2],type="b",col="Green",pch=4,ylim=c(3.7,3.8))
par(new=TRUE)
#c)
for(i in 1:length(n)){
  h=T/n[i]
  u=exp((r-(sigma^2))*h + (sigma*sqrt(h)))
  d=exp((r-(sigma^2))*h - (sigma*sqrt(h)))
  p=0.5
  price[i,3]=binum(S0,X,r,T,sigma,u,d,h,n[i],p)
}
plot(n,price[,3], type="b",col="Blue",pch=5,ylim=c(3.7,3.8))
par(new=TRUE)
#d)
sigmap=.20
for(i in 1:length(n)){
  h=T/n[i]
  u=exp(sigma*sqrt(h))
  d=exp(-sigma*sqrt(h))
  p=0.5 + 0.5*((r-((sigma^2)/2))*sqrt(h)/sigma)
  price[i,4]=binum(S0,X,r,T,sigma,u,d,h,n[i],p)
}
plot(n,price[,4],type="b",col="Purple",pch=6,ylim=c(3.7,3.8))
```


#2

```{r}
#question 2
library(plyr)
setwd("C:/Users/garim/OneDrive/Documents/My ucla/q3/computational methods/week 4")
google=read.csv("Google.csv")
N=nrow(google)
S0=google$Adj.Close[1]

r <- .02
X <- round_any(S0*1.1,10)
T <- 8.5/12 #from may to jan, I have considered as nine months
google$Date= as.Date(google$Date,"%m/%d/%y")

ret=((google$Adj.Close[1:(N-1)])/google$Adj.Close[2:N])-1
std=sd(ret)
sigma=.203
sigma=std*sqrt(252)
n=500
h=T/n
c=0.5*(exp(-r*h)+exp((r+(sigmap^2))*h))
d=c- sqrt((c^2)-1)
u=1/d
p=(exp(r*h)-d)/(u-d)
pricec=binum(S0,X,r,T,sigma,u,d,h,n,p)

#23.9
actual_call=23.9
i=.15
while(i<sigma){
  c=0.5*(exp(-r*h)+exp((r+(i^2))*h))
  d=c- sqrt((c^2)-1)
  u=1/d
  p=(exp(r*h)-d)/(u-d)
  price=binum(S0,X,r,T,i,u,d,h,n,p)
  if((price-actual_call)>0){
    break
  }else{
    i=i+0.002
  }
}

```

Price of my option is coming out to be `r toString(pricec)`

Price given online is 23.9

The reason behind the difference is the fact that Implied volatility is usually different that the historical volatility as we assumed. This is due to structural impacts and v=market's perception of future of Google. We only took in account the past effects but not future goals.

The Implied we are getting by using 23.9 as our call price is `r i`.

#3

```{r}
S0 =49
X = 50
r = 0.03
sigma = 0.2
T = 0.3846
mu=.14
n=500

h=T/n
u=exp((r-(sigma^2))*h + (sigma*sqrt(h)))
d=exp((r-(sigma^2))*h - (sigma*sqrt(h)))
p=0.5

s=matrix(nrow=31,ncol=2)
call=matrix(nrow=31,ncol=2)
j=1
for(i in 20:80){
  if(i%%2==0){
    s[j,1]=i
    s[j,2]=i+0.01
    j=j+1
  }
}

for(i in 1:31){
  call[i,1]=binum(s[i,1],X,r,T,sigma,u,d,h,n,p)
  call[i,2]=binum(s[i,2],X,r,T,sigma,u,d,h,n,p)
}

delta=(call[,1]-call[,2])/(s[,1]-s[,2])

plot(s[,1],delta,type="b",pch=1,col="Blue",lwd=3,ylab="Delta",xlab="Stock price")



```

#b

```{r}
S0=49
t1=0
t=matrix(nrow=39,ncol=2)
call=matrix(nrow=39,ncol=2)
j=1
while(t1<=T){
  
    t[j,1]=t1
    t[j,2]=t1+0.001
    j=j+1
    t1=t1+0.01
  
}

for(i in 1:39){
  h=t[i,1]/n
  u=exp((r-(sigma^2))*h + (sigma*sqrt(h)))
  d=exp((r-(sigma^2))*h - (sigma*sqrt(h)))
  call[i,1]=binum(S0,X,r,t[i,1],sigma,u,d,h,n,p)
  call[i,2]=binum((S0-0.01),X,r,t[i,1],sigma,u,d,h,n,p)
}

delta_t=(call[,1]-call[,2])/(0.01)

plot(t[2:39,1],delta_t[2:39],type="b",pch=1,col="Green",lwd=3,ylab="Delta",xlab="Time")


```

#c

```{r}
call=matrix(nrow=31,ncol=2)
for(i in 1:31){
  h=T/n
  u=exp((r-(sigma^2))*h + (sigma*sqrt(h)))
  d=exp((r-(sigma^2))*h - (sigma*sqrt(h)))
  call[i,1]=binum(s[i,1],X,r,T,sigma,u,d,h,n,p)
  h=(T+0.001)/n
  u=exp((r-(sigma^2))*h + (sigma*sqrt(h)))
  d=exp((r-(sigma^2))*h - (sigma*sqrt(h)))
  call[i,2]=binum(s[i,1],X,r,T,sigma,u,d,h,n,p)
}

theta_s=(call[,1]-call[,2])/(0.001)

plot(s[,1],theta_s,type="b",pch=3,col="Brown",lwd=5,ylab="Theta",xlab="Stock Price")
```

#d

```{r}
gamma=(delta[2:31]-delta[1:30])/(s[2:31,1]-s[1:30,1])
plot(s[1:30,1],gamma,col="Blue",lwd=3,ylab="Gamma",xlab="Stock Price")
```

#e

```{r}
call=matrix(nrow=31,ncol=2)
sigma1=sigma-0.001
for(i in 1:31){
  h=T/n
  u=exp((r-(sigma^2))*h + (sigma*sqrt(h)))
  d=exp((r-(sigma^2))*h - (sigma*sqrt(h)))
  call[i,1]=binum(s[i,1],X,r,T,sigma,u,d,h,n,p)
  
  u=exp((r-(sigma1^2))*h + (sigma1*sqrt(h)))
  d=exp((r-(sigma1^2))*h - (sigma1*sqrt(h)))
  call[i,2]=binum(s[i,1],X,r,T,sigma1,u,d,h,n,p)
}
vega_s=vector(length = 31)
for(i in 1:31){
  vega_s[i]=max((call[i,1]-call[i,2]),0)/(0.001)
}
plot(s[,1],vega_s,type="b",pch=3,col="Brown",lwd=5,ylab="Vega",xlab="Stock Price")

```

#f

```{r}
for(i in 1:31){
  h=T/n
  u=exp((r-(sigma^2))*h + (sigma*sqrt(h)))
  d=exp((r-(sigma^2))*h - (sigma*sqrt(h)))
  call[i,1]=binum(s[i,1],X,r,T,sigma,u,d,h,n,p)
  r=r-0.0001
  u=exp((r-(sigma^2))*h + (sigma*sqrt(h)))
  d=exp((r-(sigma^2))*h - (sigma*sqrt(h)))
  call[i,2]=binum(s[i,1],X,r,T,sigma,u,d,h,n,p)
}

rho_s=(call[,1]-call[,2])/(0.0001)

plot(s[,1],rho_s,type="b",pch=3,col="Brown",lwd=5,ylab="Rho",xlab="Stock Price")
```

#4

```{r}
X = 100
r = 0.05
sigma = 0.3
T = 1
n=500
h=T/n
c=0.5*(exp(-r*h)+exp((r+(sigma^2))*h))
d=c- sqrt((c^2)-1)
u=1/d
p=(exp(r*h)-d)/(u-d)
s=matrix(nrow=11,ncol=1)
put=matrix(nrow=11,ncol=2)
j=1
for(i in 80:120){
  if(i%%4==0){
    s[j,1]=i
    j=j+1
  }
}

for(i in 1:11){
  put[i,1]=binum_p_e(s[i,1],X,r,T,sigma,u,d,h,n,p)
  put[i,2]=binum_p_a(s[i,1],X,r,T,sigma,u,d,h,n,p)
  
}

plot(s[,1],put[,1],type="l",ylim=c(0,24),col="red",ylab="Blue=American, Red=European")
par(new=TRUE)
plot(s[,1],put[,2],type="l",ylim=c(0,24),col="blue",ylab="Blue=American, Red=European")
```

The European put option price is lesser than the American put optionprice becase -there is no option to exercise earlier in a European put option.
In American put options, we always take the higher payoffs so in European the payoffs will always be lesser.

#5

#a

```{r}
trinum<-function(S0,X,r,T,sigma,u,d,h,n,pu,pm,pd){
  price=matrix(nrow = 2*(n+1),ncol=(n+1))
  option=matrix(nrow = (n+1),ncol=(2*(n+1)-1))
  price[1]=S0
  price=vector(length = (2*(n+1)-1))
  
  for(i in 1:length(price)){
    price[i]=S0*(u^(n+1-i))
    option[(n+1),(i)]=max(0,(price[i]-X))
  }
  for(i in 1:(n)){
    for(j in 1:((2*n)-(2*i)+1)){
      
      option[(n-i+1),j]=exp(-r*h)*(pu*option[(n-i+2),j] + pm*option[(n-i+2),(j+1)] + pd*option[(n-i+2),(j+2)])
    }
  }
  return (option[1,1])
  
  
}

S0 = 32
X = 30
r = 0.05
sigma = 0.24
T = 0.5
n=c(10, 20, 40, 80, 100, 200, 500)
price=matrix(nrow = length(n),ncol=1)
#a)
for(i in 1:length(n)){
  h=T/n[i]
  d = exp(-sigma*sqrt(3*h))
  u = 1/d
  pd = ( (r*h*(1-u)) +((r*h)^2) + ((sigma^2)*h) )/( (u-d) * (1-d))
  pu = ( (r*h*(1-d)) +((r*h)^2) + ((sigma^2)*h) )/( (u-d) * (u-1))
  pm = 1 - pu - pd
  price[i,1]=trinum(S0,X,r,T,sigma,u,d,h,n[i],pu,pm,pd)
}
plot(price[,1],type="b")

```

#b

```{r}
trinum_b<-function(S0,X,r,T,sigma,u,d,h,n,pu,pm,pd){
  price=matrix(nrow = 2*(n+1),ncol=(n+1))
  option=matrix(nrow = (n+1),ncol=(2*(n+1)-1))
  price[1]=S0
  price=vector(length = (2*(n+1)-1))
  
  for(i in 1:length(price)){
    price[i]=S0+(u*(n+1-i))
    option[(n+1),(i)]=max(0,(exp(price[i])-X))
  }
  for(i in 1:(n)){
    for(j in 1:((2*n)-(2*i)+1)){
      
      option[(n-i+1),j]=exp(-r*h)*(pu*option[(n-i+2),j] + pm*option[(n-i+2),(j+1)] + pd*option[(n-i+2),(j+2)])
    }
  }
  return (option[1,1])
}


S0 = 32
X = 30
r = 0.05
sigma = 0.24
T = 0.5
X0=log(S0)
n=c(10, 20, 40, 80, 100, 200, 500)
pricer=matrix(nrow=7,ncol=1)
for(i in 1:length(n)){
  h=T/n[i]
  d = (-sigma*sqrt(3*h))
  u = -d
  
  pd = ((( ((sigma^2)*h) + ((r- ((sigma^2)/2))^2)*(h^2))/(u^2)) -
          (((r- ((sigma^2)/2))*h)/u))/2
  pu = ((( ((sigma^2)*h) + ((r- ((sigma^2)/2))^2)*(h^2))/(u^2)) +
          (((r- ((sigma^2)/2))*h)/u))/2
  pm = 1- pu - pd
  pricer[i,1]=trinum_b(X0,X,r,T,sigma,u,d,h,n[i],pu,pm,pd)
}
plot(pricer[,1],type="b")
```

```{r}
plot(price[,1],type="b",ylim=c(3.64,3.75),col="Red",ylab="Price")
par(new=TRUE)
plot(pricer[,1],type="b",ylim=c(3.64,3.75),col="Blue",ylab="Price")

```

#6

```{r}

N = 500
r = 0.04
sigma = 0.2
S0 = 88
T =5
X = 100
b1 = 2
b2 = 7

h1=halton(N/2,b1)
h2=halton(N/2,b2)

z1=vector(length = N/2)
z2=vector(length = N/2)

z1=sqrt(-2*log(h1))*cos(2*pi*h2)
z2=sqrt(-2*log(h1))*sin(2*pi*h2)

z=c(z1,z2)

st=S0*exp(((r-(sigma^2)/2)*T) + (sigma*sqrt(T)*z))
n=length(st)
c1=vector(length = n)
for(i in 1:n){
c1[i]=exp(-r*T)*max(0,(st[i]-X))
}
st=S0*exp(((r-(sigma^2)/2)*T) + (sigma*sqrt(T)*(-z)))

c2=vector(length = n)
for(i in 1:n){
  c2[i]=exp(-r*T)*max(0,(st[i]-X))
}

call=(c1+c2)/2

call_price=mean(call)
```

Call price coming out is `r toString(round(call_price,3))`
