---
title: "Computational_7"
author: "Garima Agarwal"
date: "May 21, 2017"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(OptionPricing)
library(plyr)
```

#1

```{r}
efd<-function(s0,r,sigma,K,T, dx,dt,smin,smax,method){
  pu = dt*((sigma^2)/(2*dx^2) + (r-(sigma^2)/2)/(2*dx))
  pm = 1- dt*(sigma^2)/(dx^2) - r*dt
  pd = dt*((sigma^2)/(2*dx^2) - (r-(sigma^2)/2)/(2*dx))
  n=T/dt
  if(method==0){

  xmin=log(smin)
  xmax=log(smax)
  m=ceiling((xmax-xmin)/dx) + 1
  x=matrix(data=0,nrow=m,ncol=n)
  for(i in 1:m){
    x[i,]=xmax - (i-1)*dx
  }
  s=exp(x)
  }else{
    m=ceiling((smax-smin)/dx)

    
    s=matrix(data=0,nrow=m,ncol=n)
  for(i in 1:m){
    s[i,]=smax - (i-1)*dx
  }
  }
  
  a=matrix(data=0,nrow=m,ncol=m)
  for(i in 2:(m-1)){
    a[i,i-1]=pu
    a[i,i]=pm
    a[i,i+1]=pd
  }
  a[1,]=a[2,]
  a[m,]=a[(m-1),]
  

  c=matrix(data=0,nrow=m,ncol=n)
  for(i in 1:m){
    c[i,n]=max((k-s[i,n]),0)
  }
      b=matrix(data=0,nrow=m,ncol=1)
      b[m]=-dx
  for(i in (n-1):1){
    c[,i]=a%*%c[,(i+1)] + b
  }
  return(cbind(s[,1],c[,1]))
}
```

```{r}
sigma=0.2
r=0.04
s0=10
dt=h=0.002
k=10
T=0.5
smin=1
smax=19
dx=sigma*sqrt(dt)
s=c(20,27,35,43,52,62,73,84,98,112,130,150,175)
ret1=(efd(s0,r,sigma,K,T, dx,dt,smin,smax,0))
stock=ret1[s,1]
bs=vector(length = (13))
for( i in 1:length(s)){
bs[(i)]=BS_EP(.5,k,r=0.04,sigma,stock[i])[[1]]
}
table=cbind({4:16},bs,ret1[s,2],(bs-ret1[s,2])/bs)
colnames(table)<-c("Stock Price","Black-Scholes","Explicit Finite Definate","Difference")
kable(table,caption="Prices for dx=sigma*sqrt(dt)")
dx=sigma*sqrt(3*dt)
#par(new=TRUE)
ret2=(efd(s0,r,sigma,K,T, dx,dt,smin,smax,0))
s=c(12,16,21,25,31,36,42,49,56,65,75,87,101)
stock=ret2[s,1]
bs=vector(length = (13))
for( i in 1:length(s)){
bs[(i)]=BS_EP(.5,k,r=0.04,sigma,stock[i])[[1]]
}
table=cbind({4:16},bs,ret2[s,2],(bs-ret2[s,2])/bs)
colnames(table)<-c("Stock Price","Black-Scholes","Explicit Finite Definate","Difference")
kable(table,caption="Prices for dx=sigma*sqrt(3*dt)")
dx=sigma*sqrt(4*dt)
#par(new=TRUE)
ret3=(efd(s0,r,sigma,K,T, dx,dt,smin,smax,0))
s=c(10,14,18,22,27,32,37,43,49,56,65,75,88)
stock=ret3[s,1]
bs=vector(length = (13))
for( i in 1:length(s)){
bs[(i)]=BS_EP(.5,k,r=0.04,sigma,stock[i])[[1]]
}
table=cbind({4:16},bs,ret3[s,2],((bs-ret3[s,2])/bs))
colnames(table)<-c("Stock Price","Black-Scholes","Explicit Finite Definate","Difference")
kable(table,caption="Prices for dx=sigma*sqrt(4*dt)")
par(mfrow=c(2,2))
plot(ret1,type="b",ylab="Put option price a",xlab="Stock Price",col="Red",pch=4)
plot(ret2,type="b",ylab="Put option price b",xlab="Stock Price",col="Green",pch=5)
plot(ret3,type="b",ylab="Put option price c",xlab="Stock Price",col="Blue",pch=7)

```

```{r}
ifd<-function(s0,r,sigma,K,T, dx,dt,smin,smax,method){
  pu = -dt*((sigma^2)/(2*dx^2) + (r-(sigma^2)/2)/(2*dx))
  pm = 1 + dt*(sigma^2)/(dx^2) + r*dt
  pd = -dt*((sigma^2)/(2*dx^2) - (r-(sigma^2)/2)/(2*dx))
  n=T/dt
  xmin=log(smin)
  xmax=log(smax)
  m=ceiling((xmax-xmin)/dx) + 1
  x=matrix(data=0,nrow=m,ncol=n)
  for(i in 1:m){
    x[i,]=xmax - (i-1)*dx
  }
  s=exp(x)
  a=matrix(data=0,nrow=m,ncol=m)
  for(i in 2:(m-1)){
    a[i,i-1]=pu
    a[i,i]=pm
    a[i,i+1]=pd
  }
  a[1,1]=1
  a[1,2]=-1
  a[m,(m-1)]=1
  a[m,m]=-1
  c=matrix(data=0,nrow=m,ncol=n)
  for(i in 1:m){
    c[i,n]=max((k-s[i,n]),0)
  }
  b=matrix(data=0,nrow=m,ncol=1)
  inv_a=solve(a)
  if(method==0){
  for(i in (n-1):1){
    b=c[,(i+1)]
    b[m]=dx
    b[1]=0
    c[,i]=inv_a%*%b
  }
  }

  return(cbind(s[,1],c[,1]))
}
```
```{r}
dx=sigma*sqrt(dt)
s=c(20,27,35,43,52,62,73,84,98,112,130,150,175)
ret1=(ifd(s0,r,sigma,K,T, dx,dt,smin,smax,0))
stock=ret1[s,1]
bs=vector(length = (13))
for( i in 1:length(s)){
bs[(i)]=BS_EP(.5,k,r=0.04,sigma,stock[i])[[1]]
}
table=cbind({4:16},bs,ret1[s,2],(bs-ret1[s,2])/bs)
colnames(table)<-c("Stock Price","Black-Scholes","Implicit Finite Definate","Difference")
kable(table,caption="Prices for dx=sigma*sqrt(dt)")
dx=sigma*sqrt(3*dt)
#par(new=TRUE)
ret2=(ifd(s0,r,sigma,K,T, dx,dt,smin,smax,0))
s=c(12,16,21,25,31,36,42,49,56,65,75,87,101)
stock=ret2[s,1]
bs=vector(length = (13))
for( i in 1:length(s)){
bs[(i)]=BS_EP(.5,k,r=0.04,sigma,stock[i])[[1]]
}
table=cbind({4:16},bs,ret2[s,2],(bs-ret2[s,2])/bs)
colnames(table)<-c("Stock Price","Black-Scholes","Implicit Finite Definate","Difference")
kable(table,caption="Prices for dx=sigma*sqrt(3*dt)")
dx=sigma*sqrt(4*dt)
#par(new=TRUE)
ret3=(ifd(s0,r,sigma,K,T, dx,dt,smin,smax,0))
s=c(10,14,18,22,27,32,37,43,49,56,65,75,88)
stock=ret3[s,1]
bs=vector(length = (13))
for( i in 1:length(s)){
bs[(i)]=BS_EP(.5,k,r=0.04,sigma,stock[i])[[1]]
}
table=cbind({4:16},bs,ret3[s,2],(bs-ret3[s,2])/bs)
colnames(table)<-c("Stock Price","Black-Scholes","Implicit Finite Definate","Difference")
kable(table,caption="Prices for dx=sigma*sqrt(4*dt)")
par(mfrow=c(2,2))
plot(ret1,type="b",ylab="Put option price a",xlab="Stock Price",col="Red",pch=4)
plot(ret2,type="b",ylab="Put option price b",xlab="Stock Price",col="Green",pch=5)
plot(ret3,type="b",ylab="Put option price c",xlab="Stock Price",col="Blue",pch=7)


```

```{r}
cnfdm<-function(s0,r,sigma,K,T, dx,dt,smin,smax,method){
  pu = -dt*((sigma^2)/(4*dx^2) + (r-(sigma^2)/2)/(4*dx))
  pm = 1 + dt*(sigma^2)/(2*dx^2) + (r*dt/2)
  pd = -dt*((sigma^2)/(4*dx^2) - (r-(sigma^2)/2)/(4*dx))
  n=T/dt
   if(method==0){
  xmin=log(smin)
  xmax=log(smax)
  m=ceiling((xmax-xmin)/dx) + 1
  x=matrix(data=0,nrow=m,ncol=n)
  for(i in 1:m){
    x[i,]=xmax - (i-1)*dx
  }
  s=exp(x)
  }
  a=matrix(data=0,nrow=m,ncol=m)
  for(i in 2:(m-1)){
    a[i,i-1]=pu
    a[i,i]=pm
    a[i,i+1]=pd
  }
  a[1,1]=1
  a[1,2]=-1
  a[m,(m-1)]=1
  a[m,m]=-1
  c=matrix(data=0,nrow=m,ncol=n)
  for(i in 1:m){
    c[i,n]=max((k-s[i,n]),0)
  }
  b=matrix(data=0,nrow=m,ncol=1)
  inv_a=solve(a)
  if(method==0){
  for(i in (n-1):1){
    b=matrix(data=0,nrow=m,ncol=1)
    b[m]=dx
    b[1]=0
    for(j in 2:(m-1)){
      b[j]=-pu*c[j-1,i+1]-(pm-2)*c[j,i+1]-pd*c[j+1,i+1]
    }
    c[,i]=inv_a%*%b
  }
  }
  return(cbind(s[,1],c[,1]))
}
```

```{r}
dx=sigma*sqrt(dt)
s=c(20,27,35,43,52,62,73,84,98,112,130,150,175)
ret1=(cnfdm(s0,r,sigma,K,T, dx,dt,smin,smax,0))
stock=ret1[s,1]
bs=vector(length = (13))
for( i in 1:length(s)){
bs[(i)]=BS_EP(.5,k,r=0.04,sigma,stock[i])[[1]]
}
table=cbind({4:16},bs,ret1[s,2],(bs-ret1[s,2])/bs)
colnames(table)<-c("Stock Price","Black-Scholes",
                   "Crank-Nicolson Finite Definate","Difference")
kable(table,caption="Prices for dx=sigma*sqrt(dt)")
dx=sigma*sqrt(3*dt)
#par(new=TRUE)
ret2=(cnfdm(s0,r,sigma,K,T, dx,dt,smin,smax,0))
s=c(12,16,21,25,31,36,42,49,56,65,75,87,101)
stock=ret2[s,1]
bs=vector(length = (13))
for( i in 1:length(s)){
bs[(i)]=BS_EP(.5,k,r=0.04,sigma,stock[i])[[1]]
}
table=cbind({4:16},bs,ret2[s,2],(bs-ret2[s,2])/bs)
colnames(table)<-c("Stock Price","Black-Scholes",
                   "Crank-Nicolson Finite Definate","Difference")
kable(table,caption="Prices for dx=sigma*sqrt(3*dt)")
dx=sigma*sqrt(4*dt)
#par(new=TRUE)
ret3=(cnfdm(s0,r,sigma,K,T, dx,dt,smin,smax,0))
s=c(10,14,18,22,27,32,37,43,49,56,65,75,88)
stock=ret3[s,1]
bs=vector(length = (13))
for( i in 1:length(s)){
bs[(i)]=BS_EP(.5,k,r=0.04,sigma,stock[i])[[1]]
}
table=cbind({4:16},bs,ret3[s,2],(bs-ret3[s,2])/bs)
colnames(table)<-c("Stock Price","Black-Scholes",
                   "Crank-Nicolson Finite Definate","Difference")
kable(table,caption="Prices for dx=sigma*sqrt(4*dt)")
par(mfrow=c(2,2))
plot(ret1,type="b",ylab="Put option price a",xlab="Stock Price",col="Red",pch=4)
plot(ret2,type="b",ylab="Put option price b",xlab="Stock Price",col="Green",pch=5)
plot(ret3,type="b",ylab="Put option price c",xlab="Stock Price",col="Blue",pch=7)
```

As we see that the errors are relatively small by all the methods as compared to the Blach-scholes price.
Both the Explicit Finite Difference Method and the Implicit Finite Difference Methods have the same accuracy. The accuracy of the CNFD method is more. The CNFD performs the best.
The major difference is in the stability. The EFD is an unstable scheme whereas both the IFD and the CNFD method are unconditionally stable and convergent.
The CNFD method converges faster.

#2

#EFD
```{r efd_a}
efd_a<-function(s0,r,sigma,K,T, ds,dt,smin,smax){
  n=ceiling((smax-smin)/ds)
  h=dt
  m=T/dt
  s=matrix(data=0,nrow=n,ncol=m)
  for(i in 1:n)
  {
    s[i,]=smax-(i-1)*ds
  }
  N=n
  a=matrix(data=0,nrow=n,ncol=n)
  for(i in 2:(n-1)){
    a[i,i-1]   = dt*(r*((n-i+1)/2)+ (sigma^2)*((n-i+1)^2)/2)
    a[i,i] = 1 - dt*(( (sigma^2)*((n-i+1)^2) )+ r)
    a[i,i+1] = dt*(-r*(n-i+1)/2 + (sigma^2)*((n-i+1)^2)/2)
  }
  a[1,]=a[2,]
  a[n,]=a[(n-1),]
  f_put=matrix(data=0,nrow=n,ncol=m)
  ev_put=pmax(k-s[,m],0)
  f_put[,m]=ev_put
  ecv_put=matrix(data=0,nrow=n,ncol=1)
  b_put=matrix(data=0,nrow=n,ncol=1)
  
  f_call=matrix(data=0,nrow=n,ncol=m)
  ev_call=pmax(s[,m]-k,0)
  f_call[,m]=ev_call
  ecv_call=matrix(data=0,nrow=n,ncol=1)
  b_call=matrix(data=0,nrow=n,ncol=1)
  
  b_put[n]=s[(n-1),1]-s[n,1]
  b_call[1]=ds
  for(j in (m-1):1){
    ecv_put=a%*%f_put[,(j+1)] + b_put
    f_put[,j]=pmax(ecv_put,ev_put)
    
    ecv_call=a%*%f_call[,(j+1)]+b_call
    f_call[,j]=pmax(ecv_call,ev_call)
  }
  return(cbind(s[,1],f_call[,1],f_put[,1]))
}
```

```{r efd_american}

sigma=0.2
r=0.04
s0=10
dt=h=0.002
k=10
T=0.5
smin=1
smax=19
ds=1
ret1=(efd_a(s0,r,sigma,k,T, ds,dt,smin,smax))
ds=.5
ret2=efd_a(s0,r,sigma,k,T, ds,dt,smin,smax)
ds=1.5
ret3=efd_a(s0,r,sigma,k,T, ds,dt,smin,smax)
colnames(ret1)<-c("Stock Price","Call Price","Put Price")
colnames(ret2)<-c("Stock Price","Call Price","Put Price")
colnames(ret3)<-c("Stock Price","Call Price","Put Price")
kable(ret2[7:31,],caption="dS=0.5")
kable(ret1[4:16,],caption="dS=1.0")
kable(ret3[3:11,],caption="dS=1.5")
par(new=FALSE)
#par(mfrow=c(2,2))
plot(ret2[,1],ret2[,3],type="l",xlim=c(smin,smax),ylim=c(0,8),col="red",lwd=6,
     ylab="put price",main="EFD ds",xlab="Stock price")
par(new=TRUE)
plot(ret1[,1],ret1[,3],type="l",xlim=c(smin,smax),ylim=c(0,8),col="blue",lwd=4,
     ylab="put price",main="EFD ds",xlab="Stock price")
par(new=TRUE)
plot(ret3[,1],ret3[,3],type="l",xlim=c(smin,smax),ylim=c(0,8),col="green",lwd=2,
     ylab="put price",main="EFD ds",xlab="Stock price")
#kable(as.matrix(call),caption="call")
plo1=ret1
```

```{r}
plot(ret2[,1],ret2[,2],type="l",xlim=c(smin,smax),ylim=c(0,8),col="red",lwd=6,
     ylab="call price",main="EFD ds",xlab="Stock price")
par(new=TRUE)
plot(ret1[,1],ret1[,2],type="l",xlim=c(smin,smax),ylim=c(0,8),col="blue",lwd=4,
     ylab="call price",main="EFD ds",xlab="Stock price")
par(new=TRUE)
plot(ret3[,1],ret3[,2],type="l",xlim=c(smin,smax),ylim=c(0,8),col="green",lwd=2,
     ylab="call price",main="EFD ds",xlab="Stock price")
```

#IFD

```{r ifd_a}

ifd_a<-function(s0,r,sigma,k,T, dx,dt,smin,smax,method){
  n=ceiling((smax-smin)/ds)
  h=dt
  m=T/dt
  s=matrix(data=0,nrow=n,ncol=m)
  for(i in 1:n)
  {
    s[i,]=smax-(i-1)*ds
  }
  N=n
  a=matrix(data=0,nrow=n,ncol=n)
  a[1,1]=1
  a[1,2]=-1
  a[n,n]=-1
  a[n,n-1]=1
  for(i in 2:(n-1)){
    a[i,i-1]   = -dt*(r*((n-i+1)/2)+ (sigma^2)*((n-i+1)^2)/2);
    a[i,i]     = 1 + dt*(( (sigma^2)*((n-i+1)^2) )+ r);
    a[i,i+1]   = -dt*(-r*(n-i+1)/2 + (sigma^2)*((n-i+1)^2)/2);
  }
  inv_a=solve(a)
  f_put=matrix(data=0,nrow=n,ncol=m)
  ev_put=pmax(k-s[,m],0)
  f_put[,m]=ev_put
  ecv_put=matrix(data=0,nrow=n,ncol=1)
  b_put=matrix(data=0,nrow=n,ncol=1)
  
  f_call=matrix(data=0,nrow=n,ncol=m)
  ev_call=pmax(s[,m]-k,0)
  f_call[,m]=ev_call
  ecv_call=matrix(data=0,nrow=n,ncol=1)
  b_call=matrix(data=0,nrow=n,ncol=1)
  
  for(j in (m-1):1){
    b_put=f_put[,j+1]
    b_put[1]=0;
    b_put[n]=s[n,j]-s[(n-1),j]
    ecv_put=inv_a%*%b_put
    f_put[,j]=pmax(ecv_put,ev_put)
    
    b_call=f_call[,j+1]
    b_call[n]=0;
    b_call[1]=s[1,j]-s[2,j]
    ecv_call=inv_a%*%b_call
    f_call[,j]=pmax(ecv_call,ev_call)
  }
  return(cbind(s[,1],f_call[,1],f_put[,1]))

}
```

```{r}
ds=1
ret1=(ifd_a(s0,r,sigma,k,T, ds,dt,smin,smax))
ds=.5
ret2=ifd_a(s0,r,sigma,k,T, ds,dt,smin,smax)
ds=1.5
ret3=ifd_a(s0,r,sigma,k,T, ds,dt,smin,smax)
colnames(ret1)<-c("Stock Price","Call Price","Put Price")
colnames(ret2)<-c("Stock Price","Call Price","Put Price")
colnames(ret3)<-c("Stock Price","Call Price","Put Price")
kable(ret2[7:31,],caption="dS=0.5")
kable(ret1[4:16,],caption="dS=1.0")
kable(ret3[3:11,],caption="dS=1.5")
#kable(as.matrix(put))
par(new=FALSE)
#par(mfrow=c(2,2))
plot(ret2[,1],ret2[,3],type="l",xlim=c(smin,smax),ylim=c(0,8),col="red",lwd=6,
     ylab="put price",main="IFD ds",xlab="Stock price")
par(new=TRUE)
plot(ret1[,1],ret1[,3],type="l",xlim=c(smin,smax),ylim=c(0,8),col="blue",lwd=4,
     ylab="put price",main="IFD ds",xlab="Stock price")
par(new=TRUE)
plot(ret3[,1],ret3[,3],type="l",xlim=c(smin,smax),ylim=c(0,8),col="green",lwd=2,
     ylab="put price",main="IFD ds",xlab="Stock price")
#kable(as.matrix(call),caption="call")
plo2=ret1
```

```{r}
plot(ret2[,1],ret2[,2],type="l",xlim=c(smin,smax),ylim=c(0,8),col="red",lwd=6,
     ylab="call price",main="IFD ds",xlab="Stock price")
par(new=TRUE)
plot(ret1[,1],ret1[,2],type="l",xlim=c(smin,smax),ylim=c(0,8),col="blue",lwd=4,
     ylab="call price",main="IFD ds",xlab="Stock price")
par(new=TRUE)
plot(ret3[,1],ret3[,2],type="l",xlim=c(smin,smax),ylim=c(0,8),col="green",lwd=2,
     ylab="call price",main="IFD ds",xlab="Stock price")
```

#CNFDM
```{r}
cnfdm_a<-function(s0,r,sigma,K,T, dx,dt,smin,smax,method){
  n=ceiling((smax-smin)/ds)
  h=dt
  m=T/dt
  s=matrix(data=0,nrow=n,ncol=m)
  for(i in 1:n)
  {
    s[i,]=smax-(i-1)*ds
  }
  N=n
  a=matrix(data=0,nrow=n,ncol=n)
  a[1,1]=1
  a[1,2]=-1
  a[n,n]=-1
  a[n,n-1]=1
  for(i in 2:(n-1)){

    a[i,i-1]   = -dt*(r*((N-i+1)/4)+ (sigma^2)*((N-i+1)^2)/4);
    a[i,i]     = 1 + dt*(( (sigma^2)*((N-i+1)^2)/2 )+ r/2);
    a[i,i+1]   = -dt*(-r*(N-i+1)/4 + (sigma^2)*((N-i+1)^2)/4);
  }
  inv_a=solve(a)
  
  f_put=matrix(data=0,nrow=n,ncol=m)
  ev_put=pmax(k-s[,m],0)
  f_put[,m]=ev_put
  ecv_put=matrix(data=0,nrow=n,ncol=1)
  z_put=matrix(data=0,nrow=n,ncol=1)
  
  f_call=matrix(data=0,nrow=n,ncol=m)
  ev_call=pmax(s[,m]-k,0)
  f_call[,m]=ev_call
  ecv_call=matrix(data=0,nrow=n,ncol=1)
  z_call=matrix(data=0,nrow=n,ncol=1)
  for(j in (m-1):1){
    z_put[1]=0
    z_put[n]=s[n,j]-s[n-1,j]
    for(i in 2:(n-1)){
      pu = -dt*(r*((N-i+1)/4)+ (sigma^2)*((N-i+1)^2)/4)
      pm = 1 + dt*(( (sigma^2)*((N-i+1)^2)/2 )+ r/2)
      pd = -dt*(-r*(N-i+1)/4 + (sigma^2)*((N-i+1)^2)/4)
      z_put[i] = -pu*f_put[i-1,j+1]-(pm-2)*f_put[i,j+1]-pd*f_put[i+1,j+1]
    }
    ecv_put=inv_a%*%z_put
    f_put[,j]=pmax(ecv_put,ev_put)
    
    z_call[1]=s[1,j]-s[2,j]
    z_call[n]=0
    for(i in 2:(n-1)){
      pu = -dt*(r*((N-i+1)/4)+ (sigma^2)*((N-i+1)^2)/4)
      pm = 1 + dt*(( (sigma^2)*((N-i+1)^2)/2 )+ r/2)
      pd = -dt*(-r*(N-i+1)/4 + (sigma^2)*((N-i+1)^2)/4)
      z_call[i] = -pu*f_call[i-1,j+1]-(pm-2)*f_call[i,j+1]-pd*f_call[i+1,j+1]
    }
    ecv_call=inv_a%*%z_call
    f_call[,j]=pmax(ecv_call,ev_call)
  }
  return(cbind(s[,1],f_call[,1],f_put[,1]))

}
```

```{r}
ds=1
ret1=(cnfdm_a(s0,r,sigma,k,T, ds,dt,smin,smax))
ds=.5
ret2=cnfdm_a(s0,r,sigma,k,T, ds,dt,smin,smax)
ds=1.5
ret3=cnfdm_a(s0,r,sigma,k,T, ds,dt,smin,smax)
colnames(ret1)<-c("Stock Price","Call Price","Put Price")
colnames(ret2)<-c("Stock Price","Call Price","Put Price")
colnames(ret3)<-c("Stock Price","Call Price","Put Price")
kable(ret2[7:31,],caption="dS=0.5")
kable(ret1[4:16,],caption="dS=1.0")
kable(ret3[3:11,],caption="dS=1.5")
par(new=FALSE)
#par(mfrow=c(2,2))
plot(ret2[,1],ret2[,3],type="l",xlim=c(smin,smax),ylim=c(0,8),col="red",lwd=6,
     ylab="put price",main="CNDFM ds",xlab="Stock price")
par(new=TRUE)
plot(ret1[,1],ret1[,3],type="l",xlim=c(smin,smax),ylim=c(0,8),col="blue",lwd=4,
     ylab="put price",main="CNDFM ds",xlab="Stock price")
par(new=TRUE)
plot(ret3[,1],ret3[,3],type="l",xlim=c(smin,smax),ylim=c(0,8),col="green",lwd=2,
     ylab="put price",main="CNDFM ds",xlab="Stock price")
plo3=ret1
#kable(as.matrix(call),caption="call")
```

```{r}
plot(ret2[,1],ret2[,2],type="l",xlim=c(smin,smax),ylim=c(0,8),col="red",lwd=6,
     ylab="call price",main="CNDFM ds",xlab="Stock price")
par(new=TRUE)
plot(ret1[,1],ret1[,2],type="l",xlim=c(smin,smax),ylim=c(0,8),col="blue",lwd=4,
     ylab="call price",main="CNDFM ds",xlab="Stock price")
par(new=TRUE)
plot(ret3[,1],ret3[,2],type="l",xlim=c(smin,smax),ylim=c(0,8),col="green",lwd=2,
     ylab="call price",main="CNDFM ds",xlab="Stock price")
```


```{r}
plot(plo2[,1],plo2[,2],type="l",xlim=c(smin,smax),ylim=c(0,8),col="red",lwd=6,
     ylab="call price",main="ds=1",xlab="Stock price")
par(new=TRUE)
plot(plo1[,1],plo1[,2],type="l",xlim=c(smin,smax),ylim=c(0,8),col="blue",lwd=4,
     ylab="call price",main="ds=1",xlab="Stock price")
par(new=TRUE)
plot(plo3[,1],plo3[,2],type="l",xlim=c(smin,smax),ylim=c(0,8),col="green",lwd=2,
     ylab="call price",main="ds=1",xlab="Stock price")
legend('topleft',legend = c("IFD", "EFD","CNFDM"), col = c("red", "blue","green"), lty  = 1 )
```

```{r}
plot(plo2[,1],plo2[,3],type="l",xlim=c(smin,smax),ylim=c(0,8),col="red",lwd=6,
     ylab="put price",main="ds=1",xlab="Stock price")
par(new=TRUE)
plot(plo1[,1],plo1[,3],type="l",xlim=c(smin,smax),ylim=c(0,8),col="blue",lwd=4,
     ylab="put price",main="ds=1",xlab="Stock price")
par(new=TRUE)
plot(plo3[,1],plo3[,3],type="l",xlim=c(smin,smax),ylim=c(0,8),col="green",lwd=2,
     ylab="put price",main="ds=1",xlab="Stock price")
legend('topright',legend = c("IFD", "EFD","CNFDM"), col = c("red", "blue","green"), lty  = 1 )
```